Autonomous Realization of Simple Machines

### 2014-05-23 doc/paper/paper.tex
..

>>>>

The primary locomotion strategy for Golem Krang is to balance on its two wheels, keeping its
center of mass on the vertical plane through its wheel axis. Modeled as an inverted pendulum,
locomotion via balancing has a few advantages over running on both the wheels and the back caster of
the robot. First, the footprint of the robot is smaller, 54 cm front to back due to diameter
of the wheels while dynamically balancing as opposed to 86 cm when the robot is staticly grounded.
Second, the locomotion of the robot is simpler to model since the fixed caster without omnidirectional
wheels has different friction properties as the robot spins, moves forward and backward.

The position and posture control is implemented using a proportional derivative controller based on
the inertial readings that indicate the robot angle from the vertical and the wheel encoders. In
this work, we assume the environment is setup such that the locomotion can be carried out by
turning towards the goal position, moving forward and adjusting for the goal orientation - ignoring
collisions in the world. To move forward, we use a velocity profile with limits on minimum and maximum
acceleration and deceleration.

A significant aspect of the locomotion is the manipulation of heavy objects such as 15 kg cinder
blocks and 10 kg wooden plates. To enable stable dynamic balancing, the force-torque sensors
at the end-effectors of Golem Krang are used to incorporate the mass of the carried objects into
the robot model and update the center of mass position appropriately using forward kinematics. We
provide additional insights on heavy object manipulation in the experiments section, specifically
on the effect of the object inertia and mass on the system stability.

\subsection{Manipulation}
